### 2019-07-31 thesis.tex
removed the schedule that was part of the qualifying exam - now can sleep tight
* thesis.tex: Summary: got tired for today

The prospects of this research are promising. Besides including the
new effects on the time evolution of nonlinear beam-plasma interaction,
we are planning the inclusion of effects due to non-homogeneous
medium on the beam-plasma dynamics, and its implementation in the numerical
code. Furthermore, the results regarding
the electrostatic bremsstrahlung term deserve further research in order
to confirm or discard the hypothesis made in Ref. \cite{Tigik2017a}, about
the electrostatic bremsstrahlung being the underlying effect behind the
generation of suprathermal velocity distributions, which are pervasively
observed in space plasmas. The objectives above are in accordance with
the research project approved for the ``Sandwich Doctorate Program'',
that is proposed to occur under the supervision of Dr. Peter Yoon in the
University of Maryland.

\section{Schedule}
\label{sec:schedule}
The expected schedule for the remaining period of this doctoral
research is detailed below:
\begin{itemize}
\item \textbf{March to July 2018:} inclusion the new effects on
  the time evolution of nonlinear beam-plasma interaction, and of
  implementation the code for the inclusion of non-homogeneous
  medium on the beam-plasma dynamics;
\item \textbf{August 2018 to February 2019:} internship period in
  the University of Maryland, working on the further development
  of the electrostatic bremsstrahlung hypothesis;
\item \textbf{March to August of 2019:} Thesis elaboration.
\end{itemize}

>>>>

% The prospects of this research are promising. Besides including the
% new effects on the time evolution of nonlinear beam-plasma interaction,
% we are planning the inclusion of effects due to non-homogeneous
% medium on the beam-plasma dynamics, and its implementation in the numerical
% code. Furthermore, the results regarding
% the electrostatic bremsstrahlung term deserve further research in order
% to confirm or discard the hypothesis made in Ref. \cite{Tigik2017a}, about
% the electrostatic bremsstrahlung being the underlying effect behind the
% generation of suprathermal velocity distributions, which are pervasively
% observed in space plasmas. The objectives above are in accordance with
% the research project approved for the ``Sandwich Doctorate Program'',
% that is proposed to occur under the supervision of Dr. Peter Yoon in the
% University of Maryland.

% \section{Schedule}
% \label{sec:schedule}
% The expected schedule for the remaining period of this doctoral
% research is detailed below:
% \begin{itemize}
% \item \textbf{March to July 2018:} inclusion the new effects on
%   the time evolution of nonlinear beam-plasma interaction, and of
%   implementation the code for the inclusion of non-homogeneous
%   medium on the beam-plasma dynamics;
% \item \textbf{August 2018 to February 2019:} internship period in
%   the University of Maryland, working on the further development
%   of the electrostatic bremsstrahlung hypothesis;
% \item \textbf{March to August of 2019:} Thesis elaboration.
% \end{itemize}
